\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}

% Custom section command
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1.5}{*0.5}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\name}[1]{
  \begin{center}
    \Huge\textbf{#1}
  \end{center}
  \vspace{-0.5em}
  \hrule height 0.4pt width \textwidth
  \vspace{0.5em}
}
\newcommand{\contact}[5]{
  \begin{center}
    #1 | #2 | #3 \\
    #4 | #5
  \end{center}
  \vspace{-0.5em}
  \hrule height 0.4pt width \textwidth
  \vspace{0.5em}
}

\newcommand{\spacedSection}[1]{
  \vspace{0.1em}
  \section{#1}
  \vspace{1em}
}

\begin{document}

\name{Emanuel Jureczko}
\vspace{-0.5em}
\contact{+48 518 734 135}{Informatics Student}{Gliwice, Poland}{emajure27@gmail.com}{github.com/jemek27}
% {\href{mailto:emajure27@gmail.com}{emajure27@gmail.com}}{\href{https://github.com/jemek27}{github.com/jemek27}}

\vspace{-0.5em}
\begin{justify}
\textit{Third-year student with a good theoretical background and experience in low- and high-level programming.
In my free time I enjoy working on side projects to learn new technologies and develop my skills.
I am now looking to transition from personal and study projects to commercial ones, where I can apply my knowledge 
in a professional setting, contribute to real-world applications, and collaborate with a team to deliver impactful 
solutions.}
\end{justify}

\spacedSection{Areas of expertise}

\begin{minipage}[t]{0.33\textwidth}
  \begin{flushleft}
      \begin{itemize}[leftmargin=0.5cm]
          \setlength\itemsep{0.4em}
          \item Programming Languages – \textbf{Java, C, C++, C\#, Asm, SQL, Python, JavaScript}
          \item Version control - \textbf{GitHub}
      \end{itemize}
  \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.33\textwidth}
  \begin{flushleft}
      \begin{itemize}[leftmargin=0.5cm]
          \setlength\itemsep{0.4em}
          \item Backend – \textbf{Spring Boot}
          \item Frontend – \textbf{HTML, CSS, JS}
      \end{itemize}
  \end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.33\textwidth}
  \begin{flushleft}
      \begin{itemize}[leftmargin=0.5cm]
          \setlength\itemsep{0.4em}
          \item Databases – \textbf{PostgreSQL}
          \item Containers – \textbf{Docker}
      \end{itemize}
  \end{flushleft}
\end{minipage}

\vspace{1em}
\spacedSection{EXPERIENCE}

\textbf{Internship - Fullstack Developer} \hfill September 2024 \\ [0.4em]
RED Electronics \hfill \textit{Gliwice, Poland}
\begin{itemize}[leftmargin=0.5cm]
\itemsep-3pt {}
    \item Development of a web application for data visualisation and device control. 
    Project on GitHub in the Webapp repository.
    \begin{itemize}[leftmargin=0.5cm]
      \itemsep-3pt {}
          \item Frontend: HTML, CSS, JavaScript
          \item Backend: Node.js, \textbf{Python} (LoRa data input/output)
          \item Database: \textbf{PostgreSQL} 
      \end{itemize}
\end{itemize}

\spacedSection{Education}
  
\begin{itemize}[leftmargin=0.5cm]
  \itemsep-3pt {}
      \item Informatics, Silesian University of Technology Gliwice \hfill {2022 - Present}
      \item Graphic arts and digital printing technician, CKZiU Strzelce Opolskie \hfill {2018 - 2022}
\end{itemize}

\spacedSection{Languages}
  
\begin{itemize}[leftmargin=0.5cm]
  \itemsep-3pt {}
    \item German – B2/C1 (Upper Intermediate/Advanced) – TestDaF certificate: 4/4/3/4
    \item English – B2 (Upper Intermediate)
    \item Polish – Native speaker
\end{itemize}

\spacedSection{Projects}

\begin{itemize}[leftmargin=0.5cm]
  \setlength\itemsep{0.4em}
      \item \textbf{AuthBackend} \\
      A JWT authentication and authorization service.\\ [.4em]
      \textit{Tech stack:} \textbf{Java, Spring Boot, Spring Data JPA, PostgreSQL,  Docker, RESTful API, Spring Security + JWT}

      \item \textbf{TAKE} \\
      "Tworzenie Aplikacji Klasy Enterprise" (Developing Enterprise-Class Applications), 6th Semester Java REST API Group Project\\ [.4em]
      \textit{Tech stack:} \textbf{Java, Spring Boot, Spring Data JPA, RESTful API, HATEOAS, H2 Database  }
      
      \item \textbf{Gaussian Blur ASM vs C++} \\
      Developed during the 5th semester as part of an assembly language course.
      It focuses on comparing execution times between custom C++ and Assembly libraries.
      The implemented libraries apply a Gaussian blur filter to an image.\\ [.3em]
      \textit{Tech stack:} \textbf{Asm, C++, C\#}

      \item \textbf{Sudoku Solver} \\
      A Sudoku solver that mimics human-like solving strategies rather than relying on brute force. \\ [.3em]
      \textit{Tech stack:} \textbf{C++}
      
      \item \textbf{Webapp} \\
      Part of an internship project on LoRa-based communication, created at RED Electronics. 
      The project manages the reception of data and visualises it. It also allows sending control signals to the sensor unit. \\ [.3em]
      \textit{Tech stack:} \textbf{HTML, CSS, JavaScript, Node.js, Python, PostgreSQL}

      \item \textbf{Pac-Man} \\
      4th semester programming project. Own implementation of Pac-Man in SFML 2.5.1 cpp \\ [.3em]
      \textit{Tech stack:} \textbf{C++ SFML}

      \item \textbf{Console Snake} \\
      A simple Snake game running in the Windows console.  \\ [.3em]
      \textit{Tech stack:} \textbf{C}
\end{itemize}


\end{document}